% SNAS 2026 double-blind abstract submission candidate.
\documentclass[12pt,letterpaper,twoside]{article}

\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{setspace}
\doublespacing
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\hypersetup{
  pdftitle={ConstructionSafety-FaithBench Abstract},
  pdfauthor={},
  pdfsubject={Double-blind abstract submission candidate for the 5th SNAS Interdisciplinary Research Conference},
  pdfkeywords={trustworthy AI, explainable AI, vision-language models, construction safety}
}

\setlength{\parindent}{0.5in}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,LO]{\textit{ConstructionSafety-FaithBench}}
\fancyhead[RE,RO]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\setlength{\headheight}{15pt}

\begin{document}

\begin{center}
\textbf{ConstructionSafety-FaithBench: Auditing Visual-Evidence Faithfulness in Construction-Safety Vision-Language Models}
\end{center}

\begin{center}
\textbf{Abstract}
\end{center}

Construction-safety vision-language models (VLMs) are often evaluated by final answers or plausible rationales, but neither shows whether the model used rule-relevant visual evidence. This paper presents ConstructionSafety-FaithBench, a compact audit benchmark for trustworthy construction-safety AI. Each example pairs a site image with a safety rule, answer label, evidence regions, and provenance fields. The current artifact includes 163 pilot image-rule pairs, 588 scale-up candidates, four safety-rule families, deterministic baselines, a Florence-2 grounding adapter, 948 targeted and matched-random occlusion runs, and a 120-row final audit-label layer. The audit set is intentionally difficult: it prioritizes Florence/bootstrap disagreements and weak evidence overlap. On this set, Florence grounding reaches only 18.3\% answer accuracy, while a metadata-assisted bootstrap reaches 78.3\%, showing that scaffold-level validation can hide visually grounded failures. Targeted evidence occlusion changes Florence answers 39.2\% of the time versus 9.2\% for matched random masks, with a paired answer-flip gap of 30.0 percentage points. The final audit labels combine 108 role-conditioned A/B consensus rows with 12 returned adjudication decisions, so results are reported with explicit provenance rather than as unqualified human ground truth. The contribution is a reproducible measurement pipeline for evidence faithfulness, not an autonomous inspection system.

\end{document}
